parental migration and adolescents educational performance

### 2022-06-23 data/Gu-thesis-script.Rmd
writing up

Load packages
```{r}
library(tidyverse) 
library(haven)
library(fixest)
library(modelsummary)
library(MatchIt)
#library(vtable)
library(ggplot2)
#library(gtsummary)
#library(DescTools)
#knitr::opts_chunk$set(modelsummary_get="broom")
```

@@

## Matching
```{r}
m.out <- matchit(
  migr ~ cog3pl + w1ttl_100 + child.age + child.is.girl + child.health.self.rated + child.has.rural.hukou + child.number.of.sibling + child.went.to.preschool + child.had.skipped.grade + child.had.repeated.grade + child.in.boarding.school + child.is.ethnic.minority + child.educational.aspiration + parent.expectation.on.child + parent.has.white.collar.job + parent.educational.level +home.economic.resource + home.extracurricular.book + home.has.internet, 
  data = d_cl, 
  replace = T,
  ratio = 3,
  method = "nearest", 
  distance = "glm",
  exact = migr ~ ctyids
  )
fig_msmd_any <- summary(m.out) %>% plot(xlim = c(0, 0.55), position = 'right')
```

@@

```{r}
d_mo_only <- d_cl %>% drop_na(migr_mo_only)
m.out_mo_only <- 
  matchit(migr_mo_only ~ cog3pl + w1ttl_100 + child.age + child.is.girl + child.health.self.rated + child.has.rural.hukou + child.number.of.sibling + child.went.to.preschool + child.had.skipped.grade + child.had.repeated.grade + child.in.boarding.school + child.is.ethnic.minority + child.educational.aspiration + parent.expectation.on.child + parent.has.white.collar.job + parent.educational.level +home.economic.resource + home.extracurricular.book + home.has.internet, 
  data = d_mo_only, 
  replace = T,
  method = "nearest",
  distance = "glm",
  ratio = 3,
  exact = migr_mo_only ~ ctyids
  )
fig_msmd_mo_only <- summary(m.out_mo_only) %>% plot(xlim = c(0, 0.55), position = 'right')
```

@@

```{r}
d_fa_only <- d_cl %>% drop_na(migr_fa_only)
m.out_fa_only <- matchit(
  migr_fa_only ~ cog3pl + w1ttl_100 + child.age + child.is.girl + child.health.self.rated + child.has.rural.hukou + child.number.of.sibling + child.went.to.preschool + child.had.skipped.grade + child.had.repeated.grade + child.in.boarding.school + child.is.ethnic.minority + child.educational.aspiration + parent.expectation.on.child + parent.has.white.collar.job + parent.educational.level +home.economic.resource + home.extracurricular.book + home.has.internet,
  data = d_fa_only,
  replace = T,
  method = "nearest",
  distance = "glm",
  ratio = 3,
  exact = migr_fa_only ~ ctyids
  )
fig_msmd_fa_only <- summary(m.out_fa_only) %>% plot(xlim = c(0, 0.55), position = 'right')
```

@@

```{r}
d_both <- d_cl %>% drop_na(migr_both) 
m.out_both <- matchit(
  migr_both ~ cog3pl + w1ttl_100 + child.age + child.is.girl + child.health.self.rated + child.has.rural.hukou + child.number.of.sibling + child.went.to.preschool + child.had.skipped.grade + child.had.repeated.grade + child.in.boarding.school + child.is.ethnic.minority + child.educational.aspiration + parent.expectation.on.child + parent.has.white.collar.job + parent.educational.level + home.economic.resource + home.extracurricular.book + home.has.internet, 
  data = d_both, 
  method = "nearest",
  distance = "glm",
  replace = T,
  ratio = 3,
  exact = migr_both ~ ctyids
  )
fig_msmd_both <- plot(summary(m.out_both), xlim = c(0, 0.55), position = 'right')
```

>>>>

Load packages
```{r}
library(tidyverse) 
library(haven)
library(fixest)
library(modelsummary)
library(MatchIt)
#library(vtable)
library(ggplot2)
library(cobalt) 
#library(gtsummary)
#library(DescTools)
#knitr::opts_chunk$set(modelsummary_get="broom")
```

@@

## Matching
```{r}
m.out <- matchit(
  migr ~ cog3pl + w1ttl_100 + child.age + child.is.girl + child.health.self.rated + child.has.rural.hukou + child.number.of.sibling + child.went.to.preschool + child.had.skipped.grade + child.had.repeated.grade + child.in.boarding.school + child.is.ethnic.minority + child.educational.aspiration + parent.expectation.on.child + parent.has.white.collar.job + parent.educational.level +home.economic.resource + home.extracurricular.book + home.has.internet, 
  data = d_cl, 
  replace = T,
  ratio = 3,
  method = "nearest", 
  distance = "glm",
  exact = migr ~ ctyids
  )
```

```{r}
sum_m.out <- summary(m.out)
fig_msmd_any <- plot(sum_m.out, xlim = c(0, 0.55), position = 'right')
```

```{r}
love.plot(
  m.out,
  stats = "variance.ratios",
  binary = "std", 
  #limits = c(0, 0.55),
  )
```

@@

```{r}
d_mo_only <- d_cl %>% drop_na(migr_mo_only)
m.out_mo_only <- 
  matchit(migr_mo_only ~ cog3pl + w1ttl_100 + child.age + child.is.girl + child.health.self.rated + child.has.rural.hukou + child.number.of.sibling + child.went.to.preschool + child.had.skipped.grade + child.had.repeated.grade + child.in.boarding.school + child.is.ethnic.minority + child.educational.aspiration + parent.expectation.on.child + parent.has.white.collar.job + parent.educational.level +home.economic.resource + home.extracurricular.book + home.has.internet, 
  data = d_mo_only, 
  replace = T,
  method = "nearest",
  distance = "glm",
  ratio = 3,
  exact = migr_mo_only ~ ctyids
  )
```

```{r}
sum_m.out_fa_only <- summary(m.out_fa_only)
fig_msmd_fa_only <- plot(sum_m.out_fa_only, xlim = c(0, 0.55), position = 'right')
```

```{r}
love.plot(
  m.out_mo_only,
  stats = "variance.ratios",
  binary = "std", 
  #limits = c(0, 1.5),
  )
```

@@

```{r}
d_fa_only <- d_cl %>% drop_na(migr_fa_only)
m.out_fa_only <- matchit(
  migr_fa_only ~ cog3pl + w1ttl_100 + child.age + child.is.girl + child.health.self.rated + child.has.rural.hukou + child.number.of.sibling + child.went.to.preschool + child.had.skipped.grade + child.had.repeated.grade + child.in.boarding.school + child.is.ethnic.minority + child.educational.aspiration + parent.expectation.on.child + parent.has.white.collar.job + parent.educational.level +home.economic.resource + home.extracurricular.book + home.has.internet,
  data = d_fa_only,
  replace = T,
  method = "nearest",
  distance = "glm",
  ratio = 3,
  exact = migr_fa_only ~ ctyids
  )
sum_m.out_fa_only <- summary(m.out_fa_only)
fig_msmd_fa_only <- plot(sum_m.out_fa_only, xlim = c(0, 0.55), position = 'right')
```
```{r}
love.plot(
  m.out_fa_only,
  stats = "variance.ratios",
  binary = "std", 
  #limits = c(0, 0.55),
  )
```

@@

```{r}
d_both <- d_cl %>% drop_na(migr_both) 
m.out_both <- matchit(
  migr_both ~ cog3pl + w1ttl_100 + child.age + child.is.girl + child.health.self.rated + child.has.rural.hukou + child.number.of.sibling + child.went.to.preschool + child.had.skipped.grade + child.had.repeated.grade + child.in.boarding.school + child.is.ethnic.minority + child.educational.aspiration + parent.expectation.on.child + parent.has.white.collar.job + parent.educational.level + home.economic.resource + home.extracurricular.book + home.has.internet, 
  data = d_both, 
  method = "nearest",
  distance = "glm",
  replace = T,
  ratio = 3,
  exact = migr_both ~ ctyids
  )
```

```{r}
 #plot(summary(m.out_both), xlim = c(0, 0.55), position = 'right')
love.plot(
  m.out_both,
  threshold = c(m = .1),
  binary = "std", 
  limits = c(0, 0.55),
  abs = T
  )
love.plot(
  m.out_both,
  stats = "variance.ratios",
  binary = "std", 
  #limits = c(0, 0.55),
  abs = T
  )
